\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[colorinlistoftodos]{todonotes}
\pagestyle{empty}

\title{Word ladders report}
\author{Author 1 and Author 2}

\begin{document}
  \maketitle

  \section{Results}

  \todo[inline]{Briefly comment the results, did the script say all your solutions were correct? Approximately how long time does it take for the program to run on the largest input? What takes the majority of the time?}

  The script said all solutions were correct. The program takes about 16 seconds with the largest input. 
  The majority of the time is spent on making the "graph" or in our case, finding and setting neighbours to all the nodes. 

  \section{Implementation details}

  \todo[inline]{How did you implement the solution? Which data structures were used? Which modifications to these data structures were used? What is the overall running time? Why?}

  We only use nodes and their references. We send the nodes to a BFS algorithm and save the path along the way with a predicate in the node. 
  Then we backtracked from the end node to the start node using that predicate. We mostly used Sets for nodes and objects where the sequence didn't matter.
  However, we needed to use and ArrayBuffer when handling queries, because these needed to be in a specific order. 
  The overall running time for our program is approximately 45-60s, i.e. very slow. This is because of the nested for loop in the main file 
  which has a time complexity of O(n^2).

\end{document}
